\subsection{Who is our target user?}
Our project's (\textit{Magpie's}) primary target is Urban Planners. Urban
Planners are professionals responsible for the development of cities and towns,
focusing on the efficient use of land, infrastructure planning, and the creation
of sustainable and resilient communities. Our secondary target is any casual
user who is interested in amenities planning, and this includes but is not
limited to the following: Sustainability Advocates, Commuters, GIS
professionals, journalists, political advisors, and parking companies.

\subsection{Why are they important?}
Urban Planners are crucial for the holistic development of cities and towns.
They ensure that urban development is sustainable, balancing economic growth and
environmental protection. Urban planners guide cities towards more efficient
uses of land, better transport systems, and overall increasing the quality of
life of residents.

By planning for current and future needs, Urban Planners help mitigate urban
challenges such as congestion, pollution, and lack of infrastructure. Their role
is essential for ensuring that urban areas can meet the demands of growing
populations, while maintaining standard of living and environmental
sustainability.

\subsection{What problem are we solving?}
Urban Planners often face challenges with accessing and analysing data. Data is
typically siloed, making it difficult to access and analyse. This can compromise
their capacity to make informed decisions. Our project aims to address the
difficulty in accessing and analysing data, by providing a platform that
aggregates data from multiple sources.

We aim to provide Urban Planners with a tool that allows them to access this
information in a single, easy to use, platform. This will allow Urban Planners
to streamline the initial phases of their work, decreasing the time spent on
data collection and increasing the time spent on analysis and decision making.

\newpage{}