\subsubsection{Additonal Data Sources}
For future work, the most pressing task would be to add additional data sources,
in particular transportation data such as bus and luas routes, bus stops and
luas stations. Information on the water supply and the electrical infrastructure
would equally be helpful to add, in particular information pertaining to the
municipal water supply, the power grid, off the grid solar panels and backup
generators. Furthermore, the current amenities should be extended to include
more counties, close to Dublin such as Fingal, South Dublin and Meath, as well
as extended to larger cities in Ireland like Cork, Galway, Limerick and Sligo.


\subsubsection{Yolo Model Improvements}
Retraining the Yolo model on a dataset containing more manually annotated
satellite images should be explored in order to improve the model's performance
and reduce the number of false positives.

Experimenting with additional fine-tuning of the YOLO model and exploring lighter 
versions of YOLO, such as YOLOv8-nano should be explored, to see if it yields better results.

\subsubsection{General Parking Detection Improvements}

Improving the road mask's accuracy in classifying cars as on the road and parked
correctly is especially crucial, as the current misclassificatios lead to
issues afterwards particularly in the unoccupied parking detection section. It could
be interesting to test out enlarging the roads by a certain ratio, depending on
the road width to begin with in order to find a way of identifying only larger
roads with multiple lanes.

The unoccupied parking detection could be further improved by adding additional
heuristics to find the empty spots more efficiently. Moreover, the 2 cases that
were removed as too many additional spots were being detected could be refined
and implemented differently.

\newpage{}

It would be interesting to explore methods to extend the detection to be able to
identify partially occluded vehicles, as cars are often hidden behind trees, in
shadows or near the edge of the images.
